---
title: "Assignment 5"
author: "Eva Wilson"
date: "3/8/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# attach packages 
library(here)
library(purrr)
library(tidyverse)
library(testthat)
```

## Assignment Instructions 

Design a function - you can pick any subject and you can even make up the equations as long as they conceptually make sense
  Make sure it has at least 2 inputs and 1 parameter (ideally more) and at least 2 outputs
  Code your function in R, save as a R file in subdirectory called R
  Make sure you include documentation (both at the top as we’ve shown in past examples, and inline)
  Include some error checking

In an Rmarkdown file, generate some data for 2 of the function inputs
  Use a for loop to run the function for the data
  Repeat the “looping” using something from the “purrr” package
  Graph results (you can decide what the most interesting way to graph - you just need to make one graph)

Write at least 2 tests for your function; store in a separate test file

Put this in a git repo that includes an R subdirectory a tests subsdirectory and an Rmarkdown file and submit the link on Gauchospace (or you can put all of this in a new git repo or a subdirectory of an existing git repo)

## Step 1. Source function 
```{r}
here("irrigation.R")
```

## Step 2. List assumptions 

1. We assume that ET falls within a range? 
2. There are 50 fields in our analysis

## Step 3. Create data frames to test functionality
```{r}
# create vector of crop type
possible.crop = c("almond","vineyard","cotton")
# use sample to simulate a random recording of fields for analysis
possible.crop = base::sample(possible.crop, size=50, replace=T)
# possible.crop as a factor for better plotting
possible.crop = as.factor(possible.crop)
# to quickly get frequencies of different crops and to plot 
summary(possible.crop)
plot(possible.crop, col="blue")
```


# use a *for* loop to run the function for the data 



# repeat loop 

# graph results
ggplot(data = , aes(x=, y=)+
        +geom_histogram(stat="count")
         labs()


# it is act
```{r}
names(summary(testdata))
summary(testdata)["Max."]
expect_true((summary(testdata)"Max."]-summary(testdata)["Min."]>0))
```


```{r}

```

