---
title: "Assignment 3"
author: "Eva Wilson"
date: "3/6/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#attach packages
library(tidyverse)
library(purrr)
library(ggpubr)
library(ggplot2)
```

## Directions
* Add an additional super light car with mass 5,000 kg and a surface area 10m2

* Compute the mean and maximum power for Cars A, B, C and for your new car, assuming that average highway speed is 80 km/hr with a standard deviation of 10km/hr;  Use 2 different methods to compute the mean and maximum power for each car type; a) **FOR** loop and b) the **pmap** function from **purr**

* Create two boxplots (one for each method (**FOR** and **pmap**)) that show the range of power consumption (across sampled speeds) for each car type.

```{r}
#source function for auto power 
source("~/Bren/Q2/ESM 262 Computing for Environmental Science/examples/ESM_262_Examples/R/autopower.R")
```

## Set Up
For this analysis, we will use four different car types, a range of speed data and the auto power function to calculate the power required to maintain various speeds. The four different car types are as follows: 

* car A  mass 20000 kg, area 22 m^2^

* car B mass 65000 kg, area 30 m^2^

* car C mass 38000 kg area 22 m^2^

* car D mass 5000 kg and area 10m^2

Mean highway speed of data is 80 km/hr with standard deviation of 10 km/hr 

```{r}
# create dataframe for cars 
cars = data.frame(name = c("A","B","C","D"),mass=c(10000,65000,38000,5000), area = c(22,30,22,10))
```

```{r}
# create speed data sample
nsample = 200

# convert your mean speed to m/s
mean_speed = (80*.28)
speeds = rnorm(mean=mean_speed, sd=(10*.28), nsample)
summary(speeds)

# plot speed data to verify output
plot(density(speeds), ylab="Distribution of Speeds in (m/s)")
```

## Method 1: Run PMap
```{r}
# run pmap loop - various loop data are car areas and masses, using the autopower function and different speeds
powercarspmap = pmap(list(A = cars$area, m=cars$mass), auto_power, V=speeds)

# add values to data frame. 
# name columns after the car names 
powercarspmap = as.data.frame(powercarspmap, col.names=cars$name)

# turn columns to rows for easier plotting later on 
powercarspmap = powercarspmap %>% pivot_longer(cols=everything(), names_to="car", values_to="power")
```

## Method 2: For Loop
```{r}
# before running the for loop, create a data frame that has the # of rows = the # of speed data. The # of columns = the # of cars
powercarsfor = as.data.frame(matrix(nrow=length(speeds), ncol=nrow(cars)))

# add column names 
colnames(powercarsfor) = cars$name

# run the for loop and add values to data frame
for (i in 1:nrow(cars)) {
  powercarsfor[,i] = auto_power(A=cars$area[i], m=cars$mass[i], V=speeds)
}

# turn columns to rows for easier plotting 
powercarsfor = powercarsfor %>% pivot_longer(cols=everything(), names_to="car", values_to="power")
```

## Plotting
```{r}
# plotting - create two different plots based on your data 
pmap_plot = ggplot(powercarspmap, aes(car,power, fill=car))+
  geom_boxplot()+
  ggtitle("PMap Loop")+
  labs(x = "Car", y = "Power (Watts)") +
  theme_minimal()

for_plot = ggplot(powercarsfor, aes(car,power, fill=car))+
  geom_boxplot()+
  ggtitle("For Loop")+
  labs(x = "Car", y = "Power (Watts)") +
  theme_minimal()

#use the ggarrange tool to overlay 
ggarrange(pmap_plot, for_plot, nrow=2)