---
title: "Assignment 4"
author: "Eva Wilson"
date: "3/6/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# attach packages 
library(tidyverse)
library(purrr)
library(here)
```

## Assignment Instructions 

Write a function that takes a vector of fish names and always returns three items:

1. the most common fish,
2. the rarest fish
3. the total number of fish

Create an Rmarkdown to demonstrate the use of your function with fish.txt - which is under Data on ESM_262_Examples

[Data on ESM_262_Examples]{https://github.com/naomitague/ESM_262_Examples/blob/main/Data/fish.txt}

Turn in on Gauchospace what your function returns when you run with fish.txt!

## Step 1. Source your function using relative paths
```{r}
here("summarize_fish_catch.R")
```

## Step 2. Load fish.txt data in and apply the above function
```{r}
# read in your data
fish_df <- read.delim2(here("fish.txt"))

# turn df into a vector for input into function
fish <- fish_df[[1]]

# return results
results = summarize_fish_catch(fish)
results
```



