---
title: "Assignment 5"
author: "Eva Wilson, Nick McManus, and Katheryn Moya"
date: "3/8/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# attach packages 
library(here)
library(purrr)
library(tidyverse)
library(testthat)
```

## Step 1. Source function 
```{r}
source(here("R/irrigation.R"))
```

## Step 2. List assumptions 

1. **Precipitation:** We assume that precipitation is normally distributed. The mean precipitation is 2.5 mm/day with a standard deviation of 1 mm/day. 

2. **ET:** We assume that average ET for wheat is 2.04 mm/day, corn is 2.54 mm/day, and barley is 3.00 mm/day. 

3. **Possible Crops:** There are 50 fields in our analysis that are subject to the same rainfall. We assume each occurs equally (we use random sample).

## Step 3. Create data frames to run function
```{r}
### create data frame with crop types and respective ET values (mm/day)
possible_crop <- data.frame(crop_type = c("wheat","corn","barley"),
                            ET = c(2.04, 2.54, 3.00))

### generate a normal distribution of random precipitation data
### note that 10 mm converts to 0.394 inches.  
precipitation <- rnorm(50, mean = 2.5, sd = 1)
```

## Step 4. Use the *pmap* loop to run the function for the data 
```{r}
### obtain results using pmap
results <- pmap(list(crop_type = possible_crop$crop_type,
                  ET = possible_crop$ET),
             irrigation, precip = precipitation)
results

### convert results into data frame
results_df <- as.data.frame(do.call(rbind, results)) %>% 
  ## rbind makes each row correspond with crop type
  ## add names for clarity and untangling data
  add_column(crop_type = possible_crop$crop_type)

results_df

### output from pmap is nested lists (each cell of df is a list)
### b/c function outputs list of 3 values. To deal with this,
### unnest by rows (crop type) and then bind into single df

## results for wheat
wheat <- results_df %>% 
  filter(crop_type == 'wheat') %>% 
  unnest(cols = c(V1, V2, V3)) %>% 
  ## add in precip data for later graphing
  cbind(precipitation)

## results for corn
corn <- results_df %>% 
  filter(crop_type == 'corn') %>% 
  unnest(cols = c(V1, V2, V3)) %>% 
  cbind(precipitation)

## results for barley
barley <- results_df %>% 
  filter(crop_type == 'barley') %>% 
  unnest(cols = c(V1, V2, V3)) %>% 
  cbind(precipitation)

### put all data together in nice tidy format!
irrigation_results <- rbind(wheat, corn, barley) %>% 
  ## rename first thre columns to function outputs
  rename(soil_moist_avail = V1,
         should_irrigate = V2,
         irrigation_amt = V3)

irrigation_results
```

# Step 5. Graph results
```{r}
### plot the relationship between soil moisture availability and irrigation amt
### facet_wrap by crop_type 
irrigation_plot = ggplot(data = irrigation_results, aes(x= soil_moist_avail, y= irrigation_amt))+
  geom_jitter(aes(color = crop_type), size = 2, alpha = 0.7) + # better displays the points by spreading them out given our small dataset
  scale_color_manual(values = c('burlywood4', 'olivedrab4', 'darkgoldenrod3')) +
  scale_y_continuous(breaks = seq(from = 0, to = 6, by = 1)) +
  facet_wrap(~ crop_type) +
  labs(x = "Soil Moisture Availability (mm)", 
       y = "Irrigation Amount (mm)",
       title = "Crop Irrigation Requirements For Varying Soil Moisture Availability") +
  theme_bw() +
  theme(
    axis.title.x = element_text(face = 'bold', vjust = -1),
    axis.title.y = element_text(face = 'bold', vjust = 2),
    panel.grid.minor.y = element_blank(),
    panel.grid.minor.x = element_blank(),
    legend.position = "none"
  ) 
 
irrigation_plot

```
**Figure 1.** The relationship between soil moisture availability (mm) and irrigation amount (mm) for three crops: barley, corn and wheat. Soil moisture availability was calculated using precipitation and evapotranspiration rates. Here, we see that wheat is the most water intensive of the three crops.

# Step 6. Run two tests to make sure this function is working
```{r}
# source data
source(here("R/irrigation.R"))
# put your test in a file
test_file(here("tests","irrigation_works.R"))
```
