---
title: "Assignment 4"
author: "Eva Wilson"
date: "3/6/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# attach packages 
library(tidyverse)
library(purrr)
library(here)
```

## Assignment Instructions 

Write a function that takes a vector of fish names and always returns three items:

1. the most common fish,
2. the rarest fish
3. the total number of fish

Create an Rmarkdown to demonstrate the use of your function with fish.txt - which is under Data on ESM_262_Examples

[Data on ESM_262_Examples]{https://github.com/naomitague/ESM_262_Examples/blob/main/Data/fish.txt}

Turn in on Gauchospace what your function returns when you run with fish.txt!

## Step 1. Define function to summarize the characteristics of 1 fish catch
```{r}
# define function to find and output the most common fish, most rare fish, and total number of fish in the catch
summarize_fish_catch = function(fish_data){

  # check if the data input is in vector form 
  if(!is.vector(fish_data)){
    stop("Data input into this function is not in vector form")
  }
  #find the fish that is the most common
  most_common <- names(which.max(summary(as.factor(fish_data))))

  #find the fish that is the most rare
  most_rare <- names(which.min(summary(as.factor((fish_data)))))

  #find the total number of fish
  total_fish <- length(fish_data)
  
  #return outputs as a list
  return(list(most_common, most_rare, total_fish))
}
```

## Step 2. Load fish.txt data in and apply the above function
```{r}
# read in your data
fish_df <- read.delim2(here("fish.txt"))

# turn df into a vector for input into function
fish <- fish_df[[1]]

# return results
results = summarize_fish_catch(fish)
results
```



